---
title: 'ANLY 502-51: GitHub - Hello World'
author:
- Sathya Narayanan Subbaraj
- Harrisburg University Student ID - 189745
output:
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,tidy.opts=list(width.cutoff=70),tidy=TRUE, warning = FALSE)

```
<br>

##### Read Bivariate dataset
<br>
```{r }
# Read dataset 
Profit.Defects <- read.csv('Workbook_Example_Bivariate_dataset.csv')
```
<br>

##### Dataset Summary, Structure & Variables
<br>
```{r }
# Dataset Summary
summary(Profit.Defects)

# Dataset Structure
str(Profit.Defects)

# Dataset variables
colnames(Profit.Defects)

```
<br>

##### Scatter Plot using Plot(): Profit vs. Number of Defective Items.
<br>
```{r }
# Scatter Plot using Plot()
Profit.Defects.plot1 <- plot(x = Profit.Defects$Number.of.Defective.Items, y = Profit.Defects$Profit, type = "p", 
     main = " Profit vs. Number of Defective Items", 
     xlab = "Number of Defective Items" , 
     ylab = "Profit")

Profit.Defects.plot1

```
<br>

##### Scatter Plot using ggplot(): Profit vs. Number of Defective Items.
<br>
```{r }
# Scatter Plot using ggplot()
library(ggplot2)

Profit.Defects.plot2 <- ggplot(data = Profit.Defects, aes(x = Profit.Defects$Number.of.Defective.Items, 
                                  y = Profit.Defects$Profit)) +
      geom_point(color = 'steelblue') +
      ggtitle("Profit vs Number of Defective Items") +
      theme(plot.title = element_text(hjust = 0.5)) +
      xlab("Number of Defective Items") +
      ylab("Profit")

Profit.Defects.plot2

```
<br>
From the scatter plots, it can be seen that there is a negative relationship between 'Profit' and 'Number of Defective Items'. As the number of defective items increase, the profit declines.
<br>
<br>


